%-------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%-------------------------------------------------------------------------------

\vspace{1.5em} % Ensures spacing from previous section
\cvsection{Work Experience}

\begin{cventries}

  %---------------------------------------------------------
  \cventry
    {Fullstack Developer (Contract)} % Job title
    {Startup Client via Simplified (now Omnivya)} % Organization
    {Remote} % Location
    {Feb. 2024 -- Jan. 2025} % Date(s)
    {
      \begin{cvitems}
        \item {Developed fullstack art-focused web app using Spring Boot (Flyway, Spring Security with Zitadel, Spring Data JPA, metrics/tracing) and React.}
        \item {Reverse-engineered Three.js app and built a Golang-compatible API to parse and expose data.}
        \item {Delivered both admin and client-facing UIs using React; implemented landing page with AstroJS.}
        \item {Applied clean architecture and ensured production readiness.}
      \end{cvitems}
    }

  \vspace{1.2em} % 👈 Add this to prevent overlap when entries are tight

  %---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Simplified / Omnivya} % Organization
    {Remote} % Location
    {Jan. 2025 -- Present} % Date(s)
    {
      \begin{cvitems}
        \item {Contributed across fullstack in a billing \& invoicing platform (Simplifactu): React, NestJS, PostgreSQL, TypeORM, AstroJS.}
        \item {Built robust features like partial credit notes, payment receipts, country-aware forms with legal logic, and currency support.}
        \item {Refactored large codebases by isolating subdomains (invoice, quotation, credit note) for clean architecture.}
        \item {Wrote unit, integration, and E2E tests; collaborated with ops to resolve deployment issues.}
        \item {Shared daily CRs, weekly markdown progress summaries, and clarified vague requirements through strong written communication.}
      \end{cvitems}
    }

\end{cventries}
