% --- Experience ---
\cvsection{Experience}
\begin{cventries}

  \cventry
  {Full-Stack Engineer}
  {ObserveOne}
  {Remote}
  {Nov. 2025 -- Present}
  {
    \begin{cvitems}
      \item {Refactored and shipped features across the \textbf{React} frontend (\textbf{Vite}) — autopilot UI, demo recording pipeline, component extraction, dev mocks, e2e tests.}
      \item {Built features for the \textbf{TypeScript CLI} (npm package) — api-key rotate, suite CI integration, incident management, export/import, multiple releases.}
      \item {Contributed to the \textbf{Express.js} backend — security audit (RLS policies, RPC hardening), autopilot refactor, team resource sharing, suite APIs.}
      \item {Developed the \textbf{Next.js} marketing site — semantic color tokens, branded components, light-mode fixes, /workers sub-landing, community tools.}
      \item {Architected a self-hosted distributed monitoring engine in \textbf{Bun/Hono} — 8 probe types (HTTP, Playwright browser, TCP, UDP, DB liveness, TLS, Heartbeat), multi-region master-agent architecture, Redis pub/sub \textbf{SSE} replacing dashboard polling, multi-stage Docker images.}
      \item {Built an \textbf{admin dashboard} (\textbf{React}) — Google indexing dashboard, creators/invites, alerts history, demo secret codes.}
      \item {Built a programmatic video generation pipeline with \textbf{Remotion} — story-aware zoom strategy, per-clip transitions, click sound effects.}
    \end{cvitems}
  }


  \cventry
  {Freelance Full-Stack / Mobile Developer}
  {Self-Employed}
  {Remote / Algiers}
  {Sep. 2025 -- Present}
  {
    \begin{cvitems}
      \item {Refactored and simplified \textbf{OAuth} login flows in \textbf{React Native + Expo} — cleaned up auth logic and fixed edge cases.}
      \item {Set up \textbf{Expo push notifications} with \textbf{Express} backend — end-to-end working.}
      \item {Migrated \textbf{JavaScript} codebases to \textbf{TypeScript}, separated UI from business logic, built shared components across React Native, Next.js, and Express projects.}
      \item {Built a profile import/migration feature for a link-in-bio platform — \textbf{Playwright} scrapers, \textbf{Redis} queue, \textbf{NestJS} backend, \textbf{React} frontend, e2e tests.}
    \end{cvitems}
  }

  \cventry
  {Full-Stack Developer}
  {Omnivya}
  {Remote}
  {Jan. 2024 -- Aug. 2025}
  {
    \begin{cvitems}
      \item {Designed and refactored responsive web interfaces using \textbf{React}, \textbf{TypeScript}, \textbf{AstroJS}, and \textbf{TanStack Router}.}
      \item {Built maintainable and performant UI components with \textbf{Tailwind CSS}.}
      \item {Developed secure authentication flows and role management with \textbf{Zitadel} and \textbf{BetterAuth}.}
      \item {Developed and optimized RESTful APIs with \textbf{NestJS} and \textbf{Spring Boot} to support SaaS frontend needs.}
      \item {Implemented unit, integration, and end-to-end tests (\textbf{Vitest}, \textbf{Playwright}, \textbf{TestContainers}) to ensure code reliability and production quality.}
      \item {Contributed to \textbf{CI} pipelines and monorepo tooling (\textbf{Nx}, \textbf{moonrepo}).}
    \end{cvitems}
  }

\end{cventries}
